Using Metric Space Indexing for Complete and Efficient Record Linkage

### 2017-11-21 paper.tex
Update on Overleaf.

\begin{figure}
\includegraphics[width=\textwidth]{figures/plotLQ_--_Cora_-_Brute_Force.png}
\caption{Linkage Quality using Brute Force linking on the Cora dataset\label{fig-cora-brute}}
\end{figure}

In the traditional blocking experiment the following fields from the Cora dataset are used as individually as blocking keys: \textit{author}, \textit{title}, \textit{venue}, \textit{location}, \textit{publisher} and \textit{year}. We also use a combined blocking key comprising these fields.

\Cref{comparison-of-results-cora} shows the results of the Cora experiments. The table shows the parameters for the experiment, the number of distance comparisons made, the precision, recall and the F1 measure achieved by each algorithm.  The linker column may be interpreted as follows: the algorithm name is followed by its parameters, for LSH this is the number of the bands followed by the size of bands. For traditional blocking the parameters are the fields used for blocking.

As can be seen in \Cref{comparison-of-results-cora}, M-tree reports the same results as brute-force....

\emph{\textbf{TODO: discuss measures used. num comparisons, time? etc.}}

\begin{table}[ht]
\centering
\begin{tabular}{l|r|r|r|r}
\parbox{0.2\textwidth}{\centering Linker} &
\parbox{0.2\textwidth}{\centering Comparisons} &
\parbox{0.17\textwidth}{\centering Precision} &
\parbox{0.17\textwidth}{\centering Recall} &
\parbox{0.17\textwidth}{\centering F1 Measure} \\ \hline \hline
Brute Force        & 1,677,025                 & 0.84      & 0.57   & 0.68       \\ \hline
MTree              &  902,693                  & 0.84      & 0.57   & 0.68       \\ \hline
LSH-2-2            &  192,199	& 0.95	& 0.47	& 0.63       \\
LSH-5-2            &  342,849	& 0.91	& 0.55	& 0.69       \\
LSH-10-2           &  513,947	& 0.88	& 0.57	& 0.69       \\
LSH-2-5            &  14,329	& 0.99	& 0.28	& 0.43      \\
LSH-5-5            &  22,057	& 0.99	& 0.36	& 0.53       \\
LSH-10-5           &  26,167	& 0.98	& 0.4	& 0.57      \\
LSH-2-10           &  4,711	& 1	& 0.15	& 0.27    \\
LSH-5-10           &  6,501	& 1	& 0.19	& 0.32      \\
LSH-10-10          & 10,627  	& 0.99	& 0.27& 	0.43       \\  \hline
Block-year         &  115,893                  & 0.99      & 0.35   & 0.51       \\
Block-authors      &   11,039                   & 0.94      & 0.16   & 0.28       \\
Block-title        &   27,407                   & 0.95      & 0.42   & 0.58       \\
Block-venue        &   36,647                   & 0.85      & 0.29   & 0.44       \\
Block-location     & 1,009,957                 & 0.83      & 0.43   & 0.57       \\
Block-publisher    &  833,079                  & 0.85      & 0.44   & 0.58       \\
Block-combined     & 1,214,269                 & 0.84      & 0.56   & 0.67       \\ \hline
\end{tabular}
\caption{Linkage Quality on the Cora dataset distance=70\label{comparison-of-results-cora}
\textbf{TODO: The table needs some rows removed. Note that this table is with a threshold value of 70.}
}
\end{table}

@@

@@

LSH-10-5 & 129,873                    & 0.72      & 0.01   & 0.02       \\ \hline
\end{tabular}
\caption{Linkage Quality on demography datasets \textbf{This is for Skye. Threshold value is 2.}
\label{comparison-of-results-demography-skye}
}
\end{table}

\Cref{comparison-of-results-demography-skye} and \Cref{comparison-of-results-demography-kili} shows the results for LSH-Minhash and M-tree applied to The Isle of Skye and Kilmarnock datasets. The shingle-size was set to 2 for all the LSH experiments shown as this was found to give good results and LSH was not especially sensitive to this parameter. Results for other shingle sizes were omitted from this paper for brevity. In these experiments the linkage performed is between birth and death records. In both cases the F1 measure achieved is better for M-tree than any of the experimental settings chosen for LSH. This is largely due to the recall for M-tree being much higher than any of the LSH experiments. For all LSH parameters LSH out performs M-tree in terms of precision.

\begin{table}[ht]
\centering
\begin{tabular}{l|r|r|r|r|r|r}
\parbox{0.2\textwidth}{\centering Linker} &
\parbox{0.2\textwidth}{\centering Comparisons} &
\parbox{0.17\textwidth}{\centering Precision} &
\parbox{0.17\textwidth}{\centering Recall} &
\parbox{0.17\textwidth}{\centering F1 Measure} \\ \hline \hline
MTree     & 514,871,153                   & 0.76      & 0.45   & 0.57      \\ \hline
LSH-2-2   & 99,145,887                    & 0.81      & 0.16   & 0.27       \\
LSH-5-2   & 130,721,338                   & 0.79      & 0.23   & 0.36       \\
LSH-10-2  & 177,168,848                   & 0.79      & 0.36   & 0.49       \\
LSH-5-5   & 239,368                      & 0.84      & 0.01   & 0.02       \\
LSH-10-5  & 855,431                      & 0.87      & 0.02   & 0.03 \\ \hline
\end{tabular}
\caption{Linkage Quality on demography datasets\textbf{This is for Kilmarnock. Threshold value is 2.}
\label{comparison-of-results-demography-kili}
}
\end{table}

@@

\emph{IS THIS RIGHT?}.

>>>>

\begin{figure}
\centering
\begin{subfigure}{.5\textwidth}
  \centering
\includegraphics[width=\textwidth]{figures/plotLQ-cora-brute}
\caption{Cora - Brute Force}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
\includegraphics[width=\textwidth]{figures/plotLQ-cora-mtree}
\caption{Cora - M-Tree}
\end{subfigure}

\begin{subfigure}{.5\textwidth}
  \centering
\includegraphics[width=\textwidth]{figures/plotLQ-cora-trad-authors}
\caption{Cora - Traditional Blocking on the `authors' field}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
\includegraphics[width=\textwidth]{figures/plotLQ-cora-trad-title}
\caption{Cora - Traditional Blocking on the `title' field}
\end{subfigure}

\begin{subfigure}{.5\textwidth}
  \centering
\includegraphics[width=\textwidth]{figures/plotLQ-cora-trad-year}
\caption{Cora - Traditional Blocking on the `publication year' field}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
\includegraphics[width=\textwidth]{figures/plotLQ-cora-trad-combined}
\caption{Cora - Traditional Blocking using the union of blocking on all fields}
\end{subfigure}

\begin{subfigure}{.5\textwidth}
  \centering
\includegraphics[width=\textwidth]{figures/plotLQ-cora-lsh-2-2}
\caption{Cora - LSH Blocking using 2 bands of size 2}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
\includegraphics[width=\textwidth]{figures/plotLQ-cora-lsh-2-10}
\caption{Cora - LSH Blocking using 2 bands of size 10}
\end{subfigure}

\begin{subfigure}{.5\textwidth}
  \centering
\includegraphics[width=\textwidth]{figures/plotLQ-cora-lsh-10-2}
\caption{Cora - LSH Blocking using 10 bands of size 2}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
\includegraphics[width=\textwidth]{figures/plotLQ-cora-lsh-10-10}
\caption{Cora - LSH Blocking using 10 bands of size 10}
\end{subfigure}

\caption{Linkage results on the Cora data set}
\label{demography-quality-mtree}
\end{figure}

\begin{figure}
\includegraphics[width=\textwidth]{figures/plotLQ-cora-brute}
\caption{Linkage quality using brute-force linking on the Cora dataset\label{fig-cora-brute}}
\end{figure}

In the traditional blocking experiment the following fields from the
Cora dataset are used individually as blocking keys: \textit{author},
\textit{title}, \textit{venue}, \textit{location}, \textit{publisher}
and \textit{year}. We also use a combined blocking key comprising all
fields.

\Cref{comparison-of-results-cora} shows the results of the Cora
experiments. The table shows the parameters for the experiment, the
number of distance comparisons made, the precision, recall and the F1
measure achieved by each algorithm.  In the \emph{Linker} column the algorithm name is followed by its
parameters: for LSH the number of the bands followed by the band size, and for traditional blocking the fields used
for blocking.

M-tree yields the same linkage quality as brute-force, although using a significantly lower
number of comparisons.

\begin{table}[ht]
\centering
\begin{tabular}{l|r|r|r|r}
\parbox{0.2\textwidth}{\centering Linker} &
\parbox{0.2\textwidth}{\centering Comparisons} &
\parbox{0.17\textwidth}{\centering Precision} &
\parbox{0.17\textwidth}{\centering Recall} &
\parbox{0.17\textwidth}{\centering F1 Measure} \\ \hline \hline
Brute Force        & 1,677,025                 & 0.84      & 0.57   & 0.68       \\ \hline
MTree              &  902,693                  & 0.84      & 0.57   & 0.68       \\ \hline
LSH-2-2            &  192,199	& 0.95	& 0.47	& 0.63       \\
LSH-5-2            &  342,849	& 0.91	& 0.55	& 0.69       \\
LSH-10-2           &  513,947	& 0.88	& 0.57	& 0.69       \\
LSH-2-5            &  14,329	& 0.99	& 0.28	& 0.43      \\
LSH-5-5            &  22,057	& 0.99	& 0.36	& 0.53       \\
LSH-10-5           &  26,167	& 0.98	& 0.4	& 0.57      \\
LSH-2-10           &  4,711	& 1	& 0.15	& 0.27    \\
LSH-5-10           &  6,501	& 1	& 0.19	& 0.32      \\
LSH-10-10          & 10,627  	& 0.99	& 0.27& 	0.43       \\  \hline
Block-year         &  115,893                  & 0.99      & 0.35   & 0.51       \\
Block-authors      &   11,039                   & 0.94      & 0.16   & 0.28       \\
Block-title        &   27,407                   & 0.95      & 0.42   & 0.58       \\
Block-venue        &   36,647                   & 0.85      & 0.29   & 0.44       \\
Block-location     & 1,009,957                 & 0.83      & 0.43   & 0.57       \\
Block-publisher    &  833,079                  & 0.85      & 0.44   & 0.58       \\
Block-combined     & 1,214,269                 & 0.84      & 0.56   & 0.67       \\ \hline
\end{tabular}
\caption{Linkage quality on Cora dataset with distance threshold = 70
\label{comparison-of-results-cora}
}
\end{table}

@@

\Cref{comparison-of-results-demography-skye} and \Cref{comparison-of-results-demography-kili} show the results for LSH-Minhash and M-tree on the Skye and Kilmarnock datasets. Linkage was performed between birth and death records. The shingle size was set to 2 for all the LSH experiments reported, as this was found to give good results and LSH was not especially sensitive to this parameter. Results for other shingle sizes were omitted from this paper for brevity. In both cases the F1 measure achieved is better for M-tree than any of the experimental settings chosen for LSH. This is largely due to the recall for M-tree being much higher than any of the LSH experiments. For all LSH parameters LSH out performs M-tree in terms of precision.

@@

LSH-10-5 & 129,873                    & 0.72      & 0.01   & 0.02       \\ \hline
\end{tabular}
\caption{Linkage quality on Skye dataset with distance threshold = 2
\label{comparison-of-results-demography-skye}
}
\end{table}

%-------------------------------------------------------------------------------------

\begin{table}[ht]
\centering
\begin{tabular}{l|r|r|r|r|r|r}
\parbox{0.2\textwidth}{\centering Linker} &
\parbox{0.2\textwidth}{\centering Comparisons} &
\parbox{0.17\textwidth}{\centering Precision} &
\parbox{0.17\textwidth}{\centering Recall} &
\parbox{0.17\textwidth}{\centering F1 Measure} \\ \hline \hline
MTree     & 514,871,153                   & 0.76      & 0.45   & 0.57      \\ \hline
LSH-2-2   & 99,145,887                    & 0.81      & 0.16   & 0.27       \\
LSH-5-2   & 130,721,338                   & 0.79      & 0.23   & 0.36       \\
LSH-10-2  & 177,168,848                   & 0.79      & 0.36   & 0.49       \\
LSH-5-5   & 239,368                      & 0.84      & 0.01   & 0.02       \\
LSH-10-5  & 855,431                      & 0.87      & 0.02   & 0.03 \\ \hline
\end{tabular}
\caption{Linkage quality on Kilmarnock dataset with distance threshold = 2
\label{comparison-of-results-demography-kili}
}
\end{table}

%-------------------------------------------------------------------------------------

@@
